---
title: "Ramen Rating Project"
author: "Lin Miao"
date: "2021/6/4"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Members and Contributions:**

Lin Miao (linmiao@ucdavis.edu) : Data Cleaning and Outlier Removal; Visualizations; Statistical Analysis

Siyi Wei (sywei@ucdavis.edu):  Statistical Analysis; Interpretation and Reporting

Antonio Pelayo Ramirez (antpelayo@ucdavis.edu): Interpretation and Reporting

Billy Wang (mywang@ucdavis.edu): Results and Interpretation

Yicheng Xie (maxxie@ucdavis.edu ): Results and Interpretation

# A.Introduction

Ramen is a kind of food which is more and more popular and has shared larger and larger catering market in these decades. Handreds of kinds and brands of ramens are growing all over the world in different flavour. Thus it in interested that which kinds or brands of ramen are most popular, as well as why people prefer these kinds or brands of ramen. In this report, both visualization and numerical methods are used to investigate the questions proposed above.

To achieve this goal and construct the visualizations and models, We will explore ramen ratings data collected from“Big List” to see how brands, styles, and country of the production affect the ratings of the ramen. In this dataset, ratings of ramens are regarded as indicator of popularity and other variables such as brands, styles, and country metioned above are considered as predictors added into models. 

# B.Background

The dataset used in this report, the Ramen Rater dataset, is a product review website for the hardcore ramen enthusiast (or "ramenphile"), with over 2500 reviews to date. Each record in the dataset is a single ramen product review. Review numbers are contiguous: more recently reviewed ramen varieties have higher numbers. Brand, Variety (the product name), Country, and Style (Cup? Bowl? Tray?) are pretty self-explanatory. Stars indicate the ramen quality, as assessed by the reviewer, on a 5-point scale, which is the the response variable in this report to measure the popularity of each kinds and brands of ramens. 

The dataset is avaliable at webset (https://www.theramenrater.com/). 

# C.Questions interested

Rating is an important indicator which tell us that how high the acceptablity is for a product. Thus in tis report, rating is also regarded as an inidcator to represent how successful the products are. Thus the most questions are proposed as:  

 - Which ramen has the highest rating?
 
 - Which country does the highest rated ramen come from?
 
 - Is there any relationship between variables?

 
# D.Study Design and Methodology

In this report we are going to first clean the data, remove ourliers and NA, remove low-weight observations, then we are going to use plots (histogram, bar plot, pie plot, boxplot) to visualize the data set and find important details with different factors. Finally, we are going to build regression model and use anova and hypothesis test to detect the relationships between variables in details.

## Data cleaning

Data clearning is an important preprocess in data analysis, which is an ensurement for accurcy and robustness of the following visualization and models contructed processes. In this report, steps of data cleaning indlude `NA` detected and removed, outliers detected and removed, irrevelant predictors removed and transformation for variables if deeded.  

### (1)	Cleaning for response variable

```{r,echo=FALSE,message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(tidyverse)
#import data set
df <- read.csv("C:/Users/28019/OneDrive/Desktop/Statistics/STA 141A/data set/ramen-ratings.csv")

#rebuild the data set and change Stars and Review.. to numeric
df <- 
  df %>% 
  as_tibble() %>% 
  select(Style,Brand,Country,Stars,Review..) %>% 
  mutate(Stars = sapply(df$Stars, as.numeric)) %>% 
  mutate(Review.. = sapply(df$Review.., as.numeric)) %>% 
  mutate_at(1:3,as.factor)

str(df)

#clear unrated and 0 rating and NA
df <- df[!(df$Stars == "Unrated"),]
df <- df[!(df$Stars == 0),]
str(df)
```

In this dataset, `NA` of response variable, `Stars`, is recorded as `Unrated`, which makes all of `Stars` variable into characters. Thus the first step is remove observations with `Unrated` and transform the `Stars` variable into numeric. 

Besides, some observation is with `Stars` recorded as 0, which is abnormal due to the lowest rating should be 1. Thus to ensure reasonablity of the following visualization and models constructed these abnormal observations are also removed.

### (2) Removement of observations with low weights

```{r,echo=FALSE,message=FALSE, warning=FALSE}
#choose above 1000 reviews ramen
DF <-  dplyr::filter(df,Review..>999)
DF
```
In this datasets, number of reviews can be considered as a weights for these ratings. The ratings with large number of reviews are regarded as more important but with small number of reviews are considered as ignorable. In this report, only observations with number of reviews larger than 1000 would be retained and observations with reviews less than 1000 are regarded as ignorable and removed.

### (3) Removement of outliers

```{r,echo=FALSE,message=FALSE, warning=FALSE}
#clear outliers
star <- DF$Stars
boxplot(star)
summary(star)
IQR=4.5-3.5
low=3.5-1.5*IQR
df_final= dplyr::filter(DF,star > low)

#final clean data set
df_final
```

In this report, outliers are detected according to boxplot, in which observations with rating higher than $3rd\ quantile+1.5IQR$ and less than $1st\ quantile-1.5IQR$ are regarded as outliers. As a result, it is revealed that no ratings of these observations are higher than $3rd\ quantile+1.5IQR$ but a few of them are less than $1st\ quantile-1.5IQR$. Thus these observations are removed as outliers.

As a result, after data cleaning in which `NA`s, ignorable observation with low weights and outliers are removed, the number of observations is changed from 2580 to 1476. The cleaned dataset is not including any `NA`s and abnormal or unimportant observations.

## Visualizations and Analysis (explain each plot)

```{r,echo=FALSE,message=FALSE, warning=FALSE}
# total score distribution 
sort(table(df_final$Stars),decreasing = T)
ggplot(data = df_final, aes(x = Stars)) + geom_histogram(binwidth = 0.1,color = "black",fill = "lightblue") + ggtitle("Stars distribution of ramen")
```

Before model constructed, the first thing is to determine the distribution of response variable. In this report, histogram is used to visualize the distribution of rating. Through this histogram, we can clearly observe the general distribution of the ramen scores. We found that most of the ramen scores are between 3 and 5. Among them, there are 289 ramen scores are 4 stars, and there are 325 scores are 5 stars. Indeed, there are some outliers with lower scores. For example, 2.3-stars. Besides according to the figure, it indicates that the distribution of rating is almost a symmetric bell curve as normality expect rating is 5 star. It is because the maximum rating is 5, which cause the inflation of counts for 5 stars. Thus the count of 5-star is too high in the histogram. In summary, the response variable, `Stars`, is almost normality with high-value inflation.

```{r,echo=FALSE,message=FALSE, warning=FALSE}
sort(table(df_final$Country),decreasing = T)
sort(table(df_final$Style),decreasing = T)

ggplot(data = df_final) + geom_bar(mapping = aes(x = Style, fill = Style)) + ggtitle("Number of Styles for all ramen")

ggplot(data = df_final) + geom_bar(mapping = aes(x = Country, fill = Country)) + ggtitle("Number of Countries for all ramen")

#boxplot
boxplot(df_final$Stars~df_final$Style)
boxplot(df_final$Stars~df_final$Country)
```

The main questions of the report is focused on the popularity of remains in styles or country. Thus at first, it is interesting that how ramen distributed around the world and how styles of ramen distributed for themself. The sort of counts of observations across countries and styles are sorted above. As a result, ramen is widely popular in Asian contries and regions such as Janpan, Malaysia Taiwan and South Korea. USA is the only one of Top 5 which is not Asian country. 


As for style of ramen, it is found that the top 3 styles are absolutely dominant which include Pack, Cup and Bowl. The Pack ramen occupies about more than 60% ramen marketing. 

The counts of each style and country are visualized as bar plots and the distribution for rating across styles and countries are visualized on boxplot. As the boxplot shown, the median of Pack, Cup and Bowl, the top-3 styles, are close, which idnciates that style of ramens may not affect the rating. However boxplots for ratings across countries are indicates that median of ratings for country is changed. Thus countries may be a factor to affect the rating.

```{r,echo=FALSE,message=FALSE, warning=FALSE}
# subset 5 stars brand and bar plot
df_final_5_stars <- subset(df_final, Stars == "5")
sort(table(df_final_5_stars$Country),decreasing = T)
sort(table(df_final_5_stars$Style),decreasing = T)

ggplot(data = df_final_5_stars) + geom_bar(mapping = aes(x = Style, fill = Style)) + ggtitle("Number of Styles for 5-stars ramen")

ggplot(data = df_final_5_stars) + geom_bar(mapping = aes(x = Country, fill = Country)) + ggtitle("Number of Countries for 5-stars ramen")



slices<-c(192,64,56,8,4,1)
lbls<-c("Pack","Bowl","Cup", "Tray","Box","Bar")
pct <- round(slices/sum(slices)*100)
lbls2<-paste(lbls," ",pct,"%",sep="")
pie(slices,labels=lbls2,col=rainbow(length(lbls2)),main = "% styles for 5-stars ramen")


slices2 <- c(63,53,47,33,31,22,21,17,11,6,21)
lbls3 <- c("Japan","Malaysia","Taiwan","South Korea","Singapore", "USA","Hong Kong","Thailand", "China", "Indonesia","others")
pct <- round(slices2/sum(slices2)*100)
lbls4<-paste(lbls3," ",pct,"%",sep="")
pie(slices2,labels=lbls4,col=rainbow(length(lbls4)),main = "% countries for 5-stars ramen")
```

Furthermore, In this time, only observations with 5-star rating is retained rather than all observations for the dataset. It is found that among the ramen with a score of 5, we can conclude from bar plot that most of the ramen are packed, there are 192 packed ramen and 64 bowl ramen, and 56 cup ramen.On the other hand, from the bar plot and pie graph, on the country side, most of the 5-stars ramen are from Japan, Malaysia, Taiwan, Singapore and South Korea. This shows that Southeast Asian countries have this unique advantage in making ramen with unique flavors.

```{r,echo=FALSE,message=FALSE, warning=FALSE}
#interaction plot
par(mfrow=c(3,1))
interaction.plot(df_final$Brand,df_final$Country,df_final$Stars)
interaction.plot(df_final$Style,df_final$Country,df_final$Stars)
interaction.plot(df_final$Brand,df_final$Style,df_final$Stars)
```

Due to level of Brand and countries are too many, it is hard to find significant information on interaction plot.

## Regression models

Visualizations are directly enough but not precise enough due to without any numeric results. Thus to make the results precise and objective enough, linear regression models are constructed here.

```{r,echo=FALSE,warning=F,message=F}
# Brand with most 5 stars (Question-1)


# Style (cup, pack or bowl)
sort(
  table(
    df_final[df_final$Stars == 5.00, "Style"] 
  ), 
  decreasing = TRUE
)[1:5] # Top 5


df_final <- df_final[!(df_final$Stars == "Unrated"),]
df_final <- na.omit(df_final)
df_final$Stars <- as.numeric(as.character(df_final$Stars))

sort(
  table( # Get count of 5 star ratings for each country
    df_final[df_final$Stars == 5.00, "Country"] 
  ), 
  decreasing = TRUE
)[1:5] # Top 5
```

Before linear regression models constructed, highest rating counts are summaried into Top-5 and the result is showing above. It indicates that 5-stars counts are highest for Pack style, Yakisoba bround and Japan.

```{r,echo=FALSE,warning=F,message=F}
df_final <- df_final[!(df_final$Stars == "Unrated"),]
df_final <- na.omit(df_final)
df_final$Stars <- as.numeric(as.character(df_final$Stars))

summary(lm(Stars ~ factor(Style), data=df_final))
```

At first, the linear regression model in which rating is considered as response variable and style as predictor is constructed. As a result, it is found that coefficients of each levels of styles are not signidicant due to P values are more than 0.05. Thus rating is not affected by style according to the model.

```{r,echo=FALSE,warning=F,message=F}
brand_coef <- data.frame(
  coef(
    summary(
      lm(Stars ~ factor(Brand), data=df_final)
    )
  )[, c("Estimate", "t value", "Pr(>|t|)")]
)

brand_coef[brand_coef$Pr...t.. < 0.05,]
```

The linear regression model in which rating is considered as response variable and Brand as predictor is also constructed. As a result, it is found that P values of coefficients for brands are less than 0.05 for most of levels of brand,  which inidcates that rating is affected by brands. 

```{r,echo=FALSE,warning=F,message=F}
country_coef <- data.frame(
  coef(
    summary(
      lm(Stars ~ factor(Country), data=df_final)
    )
  )[, c("Estimate", "t value","Pr(>|t|)")]
)

country_coef[country_coef$Pr...t.. < 0.05,]
```

Finally, to investigate whether country would affect rating of ramens, the model with `Stars` as represent and `Country` as predictor is also constructed. Similarly with brand, it is revealed that P vlaues for some coefficients are less than 0.05, which indicates that rating is also affected by country significantly like brand predictor.

Then we use anova table and hypothesis test to test the relationship and interaction between variables:

```{r,echo=FALSE}
df <- 
  df_final %>% 
  as_tibble() %>% 
  mutate(Brand = fct_lump(Brand,prop = .02),
         Country = fct_lump(Country,prop = .05)) 
```

  1. Style vs Stars 
```{r}
anova(lm(data = df,Stars ~ Style))
```
As the p value is less than .05 so the relation between Stars and Style is significant.

 
  2. Brand vs Stars 
```{r}
anova(lm(data = df,Stars ~ Brand))
```
As the p value is less than .05 so the relation between Stars and Brand is significant.
 
  3. Country vs Stars Do variables have interaction? 
```{r}
anova(lm(data = df,Stars ~ Country+Country:Style+Country:Brand))
```

As the p value is less than .05 so the relation between Stars and Country is significant and there is a significant interaction between country and style, country and brand.
 
  1. Does variable Country and Brand have interaction? 
```{r}
anova(lm(data = df,Stars ~ Country:Brand))
```
As the p.value is less than .05 so the interaction between country and brand is significant.
 
  2. Does variable Country and Style have interaction? 
```{r}
anova(lm(data = df,Stars ~ Country:Style))
```
As the p.value is less than .05 so the interaction beteen country and style is significant.
 
  3. Does variable Style and Brand have interaction?
```{r}
anova(lm(data = df,Stars ~ Country:Brand))
```
As the p.value is less than .05 so the interaction between country and Brand is significant.

# E.Results and Interpretation

All the data we analyze are called ramen-ratings from Kaggle. After cleaning the data there are 1476 observations left. Japan, Malaysia, and Taiwan have the greatest number of ramen where Japan has the most ramen. From histogram “Stars distribution of ramen”, we observed that the majority of ramen scores above 3 stars. There are 325 ramen that scores 5 stars and 289 ramen that score 4 stars. From the histogram of “Number of Styles for all ramen” there are 7 styles of ramen in the observation, among them, “Pack” is the most common one. More than half (898/1476) of the ramen style is “Pack”. “Cup” and “Bowl” are less common, each having 20% and 15% overall. The rest four styles are seldom used. And from the pie plot “% styles for 5-stars ramen” 59% percent of 5 stars rating comes from “Pack”, which is almost 3 times more than the second one “Bowl” (20%).

When comparing the Brand, Nissin has the highest rating. Nissin has 76 5 stars which is much higher than the second one MyKuali which has 22 5 stars. When comparing the Style Pack has 239 5 stars rating, it is approximately 73% of the total 5 stars observations.

From the pie plot “% countries for 5-stars ramen” Japan has the most 5 stars with 19%. Then it is Malaysia with 16% and Taiwan with 14%. It has the same order as countries with the greatest number of ramens.

We use linear regression to check if there is a relationship between variables. Style and Stars have a significant relationship since the p-value is less than 0.05. Brand and Stars also have a significant relationship because their p-value is also less than 0.05. It is the same for Country and Stars too; they also have a significant relationship according to the regression model.

The interaction plot does not provide much information, so we use ANOVA to check the interaction between variables. The results show that the p-value is very small for all three ANOVA tests so we can conclude that country and Brand have interaction, country and style have interaction, and style and brand have interaction.

# F.Conclusion

Based on the analysis above, it is revealed that Yakisoba is the most popular brand which has the highest rating. In style level, Pack is most popular due to counts of 5-stars are highest. In country level, Japen is most populat due to counts of 5-stars are highest. The folloing linear regression indicates that brand and country affect rating significantly, thus the conclusion that Yakisoba in brand level and Japen in country level are popular is significant. In fact, the word "Ramen" is dirived from Japenese word, which also indicates that ramen is dominant and popular in carting markets in Japen. Besides, the linear regression models reveals that the most influential predictors affecting rating of ramens are brands and countries.

# Reference
www.kaggle.com/residentmario/ramen-ratings https://www.theramenrater.com

# Appendix

```{}
library(ggplot2)
library(dplyr)

#import data set
Ram <- read.csv("ramen-ratings.csv")

#change ratings to numeric
Ram$Stars <- as.numeric(as.character(Ram$Stars))
Ram$Review.. <- as.numeric(Ram$Review..)
str(Ram)

#clear unrated and 0 rating and NA
df <- Ram[!(Ram$Stars == "Unrated"),]
df <- Ram[!(df$Stars == 0),]
str(df)

#choose above 1000 reviews ramen
DF <-  dplyr::filter(df,Review..>999)
DF

#clear outliers
star <- DF$Stars
boxplot(star)
summary(star)
IQR=4.5-3.5
low=3.5-1.5*IQR
df_final= dplyr::filter(DF,star > low)

#final clean data set
df_final

# total score distribution 
sort(table(df_final$Stars),decreasing = T)
library(ggplot2)
ggplot(data = df_final, aes(x = Stars)) + geom_histogram(binwidth = 0.1,color = "black",fill = "lightblue") + ggtitle("Stars distribution of ramen")

sort(table(df_final$Country),decreasing = T)
sort(table(df_final$Style),decreasing = T)

ggplot(data = df_final) + geom_bar(mapping = aes(x = Style, fill = Style)) + ggtitle("Number of Styles for all ramen")

ggplot(data = df_final) + geom_bar(mapping = aes(x = Country, fill = Country)) + ggtitle("Number of Countries for all ramen")

#boxplot
boxplot(df_final$Stars~df_final$Style)
boxplot(df_final$Stars~df_final$Country)

# subset 5 stars brand and bar plot
df_final_5_stars <- subset(df_final, Stars == "5")
sort(table(df_final_5_stars$Country),decreasing = T)
sort(table(df_final_5_stars$Style),decreasing = T)

ggplot(data = df_final_5_stars) + geom_bar(mapping = aes(x = Style, fill = Style)) + ggtitle("Number of Styles for 5-stars ramen")

ggplot(data = df_final_5_stars) + geom_bar(mapping = aes(x = Country, fill = Country)) + ggtitle("Number of Countries for 5-stars ramen")



slices<-c(192,64,56,8,4,1)
lbls<-c("Pack","Bowl","Cup", "Tray","Box","Bar")
pct <- round(slices/sum(slices)*100)
lbls2<-paste(lbls," ",pct,"%",sep="")
pie(slices,labels=lbls2,col=rainbow(length(lbls2)),main = "% styles for 5-stars ramen")


slices2 <- c(63,53,47,33,31,22,21,17,11,6,21)
lbls3 <- c("Japan","Malaysia","Taiwan","South Korea","Singapore", "USA","Hong Kong","Thailand", "China", "Indonesia","others")
pct <- round(slices2/sum(slices2)*100)
lbls4<-paste(lbls3," ",pct,"%",sep="")
pie(slices2,labels=lbls4,col=rainbow(length(lbls4)),main = "% countries for 5-stars ramen")

# Brand with most 5 stars (Question-1)


# Style (cup, pack or bowl)
sort(
  table(
    df_final[df_final$Stars == 5.00, "Style"] 
  ), 
  decreasing = TRUE
)[1:5] # Top 5


df_final <- df_final[!(df_final$Stars == "Unrated"),]
df_final <- na.omit(df_final)
df_final$Stars <- as.numeric(as.character(df_final$Stars))

sort(
  table( # Get count of 5 star ratings for each country
    df_final[df_final$Stars == 5.00, "Country"] 
  ), 
  decreasing = TRUE
)[1:5] # Top 5

# Question-2
df_final <- df_final[!(df_final$Stars == "Unrated"),]
df_final <- na.omit(df_final)
df_final$Stars <- as.numeric(as.character(df_final$Stars))

summary(lm(Stars ~ factor(Style), data=df_final))

# Extract coef with significant t-score and p-value from summary
brand_coef <- data.frame(
  coef(
    summary(
      lm(Stars ~ factor(Brand), data=df_final)
    )
  )[, c("Estimate", "t value", "Pr(>|t|)")]
)

brand_coef[brand_coef$Pr...t.. < 0.05,]

# Extract coef with significant t-score and p-value from summary
country_coef <- data.frame(
  coef(
    summary(
      lm(Stars ~ factor(Country), data=df_final)
    )
  )[, c("Estimate", "t value","Pr(>|t|)")]
)

country_coef[country_coef$Pr...t.. < 0.05,]


df <- 
  df_final %>% 
  as_tibble() %>% 
  mutate(Brand = fct_lump(Brand,prop = .02),
         Country = fct_lump(Country,prop = .05)) 

anova(lm(data = df,Stars ~ Style))

anova(lm(data = df,Stars ~ Brand))

anova(lm(data = df,Stars ~ Country+Country:Style+Country:Brand))

anova(lm(data = df,Stars ~ Country:Brand))

anova(lm(data = df,Stars ~ Country:Style))

anova(lm(data = df,Stars ~ Country:Brand))
```